%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Kushal Roy
% Date : 26-09-2020
% License : MIT
%-------------------------------------

\documentclass[]{article}
\NeedsTeXFormat{LaTeX2e}

% Package Imports
\usepackage[hmargin=1.25cm, vmargin=0.7cm]{geometry}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage[absolute]{textpos}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fontspec,xltxtra,xunicode}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{tabulary}

%-------------------------------------------------- SETTINGS --------------------------------------------------

% Social profile definations
\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/roykushal/}
\def \linkedintext {roykushal}

\def \phoneicon {\faPhone}
\def \phonetext {+91 9686583136}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:rkus2007@gmail.com}
\def \emailtext {rkus2007@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/kushal-r}
\def \githubtext {kushal-r}

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}

\newcommand{\singlecol}[4]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[r]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4}
      \end{tabular}
    }
  \end{tabularx}
}

% Color definitions
\definecolor{date}{HTML}{666666}
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{headings}{HTML}{6A6A6A}
\definecolor{subheadings}{HTML}{333333}

% Set main fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Color=primary, Path = fonts/lato/]{Lato-Lig}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text, Path = fonts/raleway/]{Raleway-ExtraLight}
\newcommand{\custombold}[1]{\color{subheadings}\fontspec[Path = fonts/lato/]{Lato-Reg}\selectfont #1 \normalfont}

% Date command
\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\textblockorigin{0mm}{5mm} % start everyth
\newcommand{\lastupdated}{\begin{textblock}{60}(165,0)
\color{date}\fontspec[Path = fonts/raleway/]{Raleway-ExtraLight}\fontsize{8pt}{10pt}\selectfont
Last Updated on
\today
\end{textblock}}

% Name command
\newcommand{\namesection}[3]{
	\centering{
		\sffamily
		\fontspec[Path = fonts/lato/]{Lato-Hai}\fontsize{40pt}{10cm}\selectfont #1
		\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont #2
	}\\
    \vspace{5pt}
	\centering{\color{headings}\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{14pt}\selectfont #3}
	\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
	\vspace{-15pt}
}
\titlespacing{\section}{0pt}{0pt}{0pt}

\newcommand{\namesectiondouble}[6]{
    \begin{tabularx}{\textwidth}{Xr}
        {
          \begin{tabular}[b]{l}
            \sffamily
		    \fontspec[Path = fonts/lato/]{Lato-Hai}\fontsize{40pt}{10cm}\selectfont #1
		    \fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont #2
          \end{tabular}
        } & {
          \begin{tabular}[c]{l}
            {\color{headings}\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{14pt}\selectfont #3} \\
            {\color{headings}\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{14pt}\selectfont #4} \\
            {\color{headings}\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{14pt}\selectfont #5} \\
            {\color{headings}\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{14pt}\selectfont #6}
          \end{tabular}
        }
      \vspace{5pt}
      \end{tabularx}
      \noindent \makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
      \vspace{-15pt}
}
\titlespacing{\section}{0pt}{0pt}{0pt}

% Headings command
\titleformat{\section}{\color{headings}
\scshape\fontspec[Path = fonts/lato/]{Lato-Lig}\fontsize{16pt}{24pt}\selectfont \raggedright\uppercase}{} {0em}{}

% Subeadings command
\titleformat{\subsection}{\color{subheadings}
\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{12pt}{12pt}\selectfont\bfseries\uppercase}{}{0em}{}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsubsection}{0pt}{\parskip}{-\parskip}
\newcommand{\runsubsection}[1]{\color{subheadings}
\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{12pt}{12pt}\selectfont\bfseries\uppercase {#1} \normalfont}

% Descriptors command
\newcommand{\descript}[1]{\color{subheadings}\raggedright\scshape\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont {#1 \\} \normalfont}

% Location command
\newcommand{\location}[1]{\color{headings}\raggedright\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{10pt}{12pt}\selectfont {#1\\} \normalfont}

% Section seperators command
\newcommand{\sectionsep}[0]{\vspace{8pt}}

\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}

% Bullet Lists with fewer gaps command
\newenvironment{tightemize}{\vspace{-\topsep}\begin{itemize}\itemsep1pt \parskip0pt \parsep0pt}{\end{itemize}\vspace{-\topsep}}


%------------------------------------------------------------------------------------------------------------


\begin{document}
%-------------------------------------------------- HEADER --------------------------------------------------

\namesectiondouble{Kushal}{Roy}{\linkedin}{\github}{\phone}{\email}

%\namesection{Kushal}{Roy} { \urlstyle{same} \href{mailto:rkus2007@gmail.com}{rkus2007@gmail.com} | \ +91 9686583136}

%-------------------------------------------------- LEFT PANEL ----------------------------------------------

\begin{minipage}[t]{0.33\textwidth}

%-------------------------------------------------- EDUCATION ----------------------------------------------

    \section{Education}
    \subsection{NIT Durgapur}
    \descript{B.Tech in Computer Science Engineering}
    \location{Aug 2007 - April 2011| Durgapur, India \\Cum. GPA: 7.40 / 10.0}
    \sectionsep

    \subsection{St. Stephens School}
    \location{ISC May 2006|  Kolkata, India \\ Perc. Marks: 76.5\%}
    \sectionsep

%-------------------------------------------------- AWARDS ----------------------------------------------

    \section{Recognitions}
    \begin{tabulary}{\linewidth}{LLL}
    HPE & Making a Difference - Detection and eradication of issues in the application before even it reaching the customers, resulting in zero customer escalations during release. \\
    HPE & Bias For Action - Contributions made towards the identification and resolution of Common Vulnerabilities and Exposures (CVE) in the open source artifact that ships along with the product.
    \end{tabulary}
    \sectionsep

%-------------------------------------------------- SKILLS ----------------------------------------------
    \section{Skills}
    \subsection{Programming}
    \location{\textbf{Languages}:}
    Java (Expert) \textbullet{} Python (Intermediate) \textbullet{} C (Prior Experience) \\
    Object Oriented Design  \textbullet{} UML Modeling \textbullet{} Data Structures \textbullet{} Algorithms \\
    \location{\textbf{Tech Stacks}:}
    Spring Boot \textbullet{} JPA \textbullet{} Hibernate \textbullet{} Web Services(Spring REST) \\
    Javascript \textbullet{} JQuery \textbullet{} HTML \textbullet{} React \\
    Shell script \\
    CouchBase \textbullet{} MongoDB \textbullet{} InfluxDB  \\
    MySQL \textbullet{} Oracle \textbullet{} Postgres \\
    Rabbit MQ \\
    XML \textbullet{} JSON \\
    GSON \textbullet{} Jackson \\
    GIT \textbullet{} SVN \textbullet{} Maven \textbullet{} Jenkins \\
    Microsoft Visio \\
    JUnit5 \textbullet{} Mokito \\
    JMeter \textbullet{} JConsole \textbullet{} Eclipse Memory Analyzer \\
    Tomcat \textbullet{} Apache2 \\
    Eclipse PDT \textbullet{} Android \\
    \sectionsep

%-------------------------------------------------- LEFT PANEL END ----------------------------------------------
\end{minipage}% DO NOT REMOVE
%DO NOT REMOVE
\hfill%DO NOT REMOVE
%DO NOT REMOVE
%-------------------------------------------------- RIGHT PANEL ----------------------------------------------
%DO NOT REMOVE
\begin{minipage}[t]{0.66\textwidth}

%-------------------------------------------------- EXPERIENCE ----------------------------------------------
    \section{Experience}

    \runsubsection{PayPal}
    \descript{| Software Development Engineer - II }
    \location{Sep 2018 – Present | Chennai, IN}
    \vspace{\topsep}
    \begin{tightemize}\item Developed PayPal's first ever Data Life-cycle management application, for auditing, deployment, lineage, monitoring and metrics collection.
    Analyzing and reviewing requirements, writing design documents, estimating efforts, programming and delivering a complete end-to-end solution for the company.
    \item Implemented a rule engine for parsing SQL scripts and preventing unlawful queries getting executed.
    \item Engineered a custom health monitoring and metrics collecting  solution of all automated workflows running across company.
    \item Designed a Metrics Analyzer for autonomous SLA re-calibration using regression based machine learning model.
    \item Developed a database crawler for parsing history query logs from Teradata and linking lineage based on GIT, JIRA, ServiceNow.
    \item Retrofitted PayPal's enterprise task scheduler with a REST API gateway for limiting the number of parallel connections.
    \end{tightemize}
    \sectionsep

    \runsubsection{Hewlett Packard Enterprise R\&D}
    \descript{| Systems Software Engineer }
    \location{Jun 2015 – Sep 2018 | Bangalore, IN}
    \begin{tightemize}
    \item Developed \href{https://buy.hpe.com/us/en/synergy/synergy-management/synergy-image-streamer/synergy-image-streamer/hpe-synergy-image-streamer/p/1008615214}{HPE Synergy Image Streamer} server provisioning appliance.
    Image Streamer is a small piece of software that sits on HPE Blade Server, taking care of automated os deployment.
    \item Designed and developed an artifact manager for managing objects like personalized scripts, ISO images and volumes used during OS deployment.
    \end{tightemize}
    \sectionsep

    \runsubsection{Samsung Research India}
    \descript{| ​Senior Software Engineer}
    \location{Feb 2013 – May 2015 | Bangalore, IN }
    \begin{tightemize}
    \item Single-handedly implemented a new HID  service for emulating a game pad on a smartphone.
    \item Developed a prototype android application for utilizing the HID service.
    \item Initiated and engineered a System performance bench-marking utility for automated monitoring of CPU, DDR, GPU, Thermal and other sysfs/procfs parameters, that reduced the overall time consumption for bench-marking any device from 1.5hrs to 2min.
    \end{tightemize}
    \sectionsep

    \runsubsection{Mindtree}
    \descript{| ​Programmer Analyst}
    \location{Jun 2011 – Jan 2013 | Bangalore, IN }
    \begin{tightemize}
    \item Worked primarily on the development of Revenue Accounting Software, that generated
    sales records for various financial institutions.
    \item Revamped parts of the existing services to introduce new features.
    \item Identified potential bugs in the system writing unit test cases.
    \item Improved main code quality by fixing bugs to reduce defect count.
    \end{tightemize}
    \sectionsep

%-------------------------------------------------- RIGHT PANEL END ----------------------------------------------
\end{minipage}

\end{document}
