
\documentclass[]{kushal-resume}
\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\usepackage{hyperref} 
\makeatother

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Kushal}{Roy} { \urlstyle{same} 
\href{mailto:kushall.roy@gmail.com}{kushall.roy@gmail.com} | +91 9686583136} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{NIT  Durgapur}
\descript{B.Tech in Computer Science Engineering}
\location{Aug 2007 - April 2011| Durgapur, India \\CGPA: 7.40}
\sectionsep

\subsection{St. Stephens School}
\location{ISC May 2006|  Kolkata, India \\ Perc. Marks: 76.5\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/kushal-r}{\custombold{kushal-r}} \\
LinkedIn://  \href{https://www.linkedin.com/in/roykushal/}{\custombold{roykushal}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\subsection{Undergraduate}
Operating Systems \\
Artificial Intelligence  \\
Computer Graphics  \\
Software Engineering \\
Image Processing \\
{\footnotesize \textit{\textbf{(Research Project: Face Detection and Identification using Artificial Neural Network on MATLAB) }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
Java \textbullet{} Object Oriented Design  \textbullet{} UML Modeling \textbullet{} Data Structures \textbullet{} Algorithms \\

\location{Intermediate:}
Python \textbullet{} C \\ 

\location{Familiar:}
Spring Boot \textbullet{} JPA \textbullet{} Web Services(Spring REST) \\
Javascript \textbullet{} JQuery \textbullet{} HTML \textbullet{} React \\
Shell script \\
CouchBase \textbullet{} Influx DB \textbullet{} Apache Hive \\
MySQL \textbullet{} Oracle \textbullet{} Postgres \\
Rabbit MQ \\
Apache JMeter \\
XML \textbullet{} JSON \\
GSON \textbullet{} Jackson \\
GIT \textbullet{} SVN \textbullet{} Maven \textbullet{} Jenkins \\
Microsoft Visio \textbullet{} Lucid Charts \\
JUnit5 \textbullet{} Mokito \\
JMeter \textbullet{} JConsole \textbullet{} Eclipse Memory Analyzer \\
Tomcat \textbullet{} Jetty \\
Eclipse PDT \textbullet{} Android \textbullet{} \LaTeX \\
Machine Learning \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{PayPal}
\descript{| Individual Contributor }
\location{Sep 2018 – Present | Chennai, IN}
\vspace{\topsep}
\begin{tightemize}\item Working as part of Core Data Platform team, primarily in Java  and Spring boot to design and develop the full stack  implementation of a  framework for managing lifecycle events on  data like tracking lineage, deployment of changes, health monitoring. 
Reviewing requirements, creating design documents, estimating efforts and delivering a complete end-to-end solution for the company. 
\item Developed health monitoring application for collecting run statistics of all automated jobs running accross company.
The data collected in turn is processed and used by an autonomous SLA time recalibration engine built on regression based machine learning model.
\item Development of a database crawler for parsing all existing data in different data-sources like Teradata, Oracle DB, etc across company and finding the lineage information based on GIT commits, JIRA tickets, ServiceNow tickets.
\item Designed and developed an end-to-end application using Java and Spring Boot for accessing UC4 Workload Automation Engine api's in use by three teams across PayPal.
\end{tightemize}
\sectionsep

\runsubsection{Hewlett Packard Enterprise R\&D}
\descript{| Systems Software Engineer }
\location{Jun 2015 – Sep 2018 | Bangalore, IN}
\begin{tightemize}
\item Worked as part of Converged Data Centre Infrastructure team, developed from scratch
\href{https://buy.hpe.com/us/en/synergy/synergy-management/synergy-image-streamer/synergy-image-streamer/hpe-synergy-image-streamer/p/1008615214}{HPE Synergy Image Streamer} provisioning appliance. 
\item Designed and developed a RESTfull artefact manager using Spring boot, Shell scripting, for managing all provisioning objects like os personalization scripts, iso images of os and os volumes used during os deployment. \\
	    {\footnotesize \textit{\textbf{Awarded Making a Difference(Quality) for detection and resolution of issues in the application before even it reaching the customers, resulting in zero customer escalations. }}} \\
	    {\footnotesize \textit{\textbf{Awarded Bias For Action for contributions made towards the identification and resolution of Common Vulnerabilities and Exposures (CVE ) in the open source artefact that ships along with the product. }}}  \\
 \item Development of Rabbit MQ based communication platform for inter process communication between Image Streamer and \href{https://buy.hpe.com/us/en/synergy/synergy-management/synergy-composer/synergy-composer/hpe-synergy-composer/p/1008615209}{HPE Synergy Composer}
\end{tightemize}
\sectionsep

\runsubsection{Samsung Research India}
\descript{| ​Senior Software Engineer}
\location{Feb 2013 – May 2015 | Bangalore, IN }
\begin{tightemize}
\item As part of Android Platform Systems R\&D division worked on TouchWiz Platform.
\item Spearheaded the development of a new HID  service for emulating a gamepad on a smartphone.
\item Developed Proof Of Concept (PoC) android application for utilizing the HID service.
\item Initiated and developed a System performance benchmarking tool for monitoring CPU, DDR, GPU, Thermal and other sysfs/procfs parameters, that reduced the overall time consumption for benchmarking any device from 1.5hrs to 2mins.
\end{tightemize}
\sectionsep

\runsubsection{Mindtree}
\descript{| ​Programmer Analyst}
\location{Jun 2011 – Jan 2013 | Bangalore, IN }
\begin{tightemize}
\item Was part of BFSI domain, worked primarily on the development of Revenue Accounting Software that generated
 sales data for various financial institution. 
 \item Improved main code quality by fixing bugs to reduce defect count.
\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}